---
title: "josh_file"
author: "doraaobodo"
date: "2020-07-13"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Introduction

I will be trying to analyze the NAICS Code and how much different industries might have received. I will group businesses in Tennessee by their codes and use an API to retrieve code names.

## Load data

The first thing to do is to load data from Tennessee. Single state folders contain a .csv for small businesses who recieved loans up to 150k. Data for **ALL** states >150k should be downloaded from [here](https://www.dropbox.com/s/e7hfn71g0hnuelk/foia_150k_plus.csv?dl=0).

```{r load libraries}
library(data.table)
library(ggplot2)
```


```{r laod all data}


dataDir = 'data'
stateDir = 'Tennessee'

naics_codes = fread(file.path(dataDir, '2-6 digit_2017_Codes.csv'))

all_states_plus = fread(file.path(dataDir, 'foia_150k_plus.csv'))
tn_1 = fread(file.path(dataDir, stateDir, 'foia_up_to_150k_TN.csv'))
```

```{r head all_states_plus}
head(all_states_plus, 3)
```

```{r head kentucky only}
head(tn_1, 3)
```

There's a more information provided for busines that recieved more loans. We also want to add the NAICS codes to the frames.

## A Little Processing
```{r process_data}
all_states_plus[, BusinessName := NULL]
all_states_plus[, Address := NULL]
setnames(all_states_plus, 'LoanRange', 'LoanAmount')

tn_2 = all_states_plus[State == 'KY']
tn_dat = rbind(tn_1, tn_2)
# tn_dat_naics = merge(tn_dat, naics_codes, by="NAICSCode")
```

## See Head

```{r plot trend}
top20 = head(tn_dat,20)
```

# Make plot

```{r plot trend}
ggplot(top20, aes(x = "2017 NAICS US Title", y = LoanAmount, fill = NAICSCode)) + geom_boxplot(alpha = 0.1) + theme(axis.text = element_text(color = 'black')) + labs(title = 'Small Business Loan Amount by NAICS Code for all Loans')
```

