---
title: "Sample Analysis for SBA Dataset"
author: "doraaobodo"
date: "2020-07-13"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Introduction

ALL data files are located within the `data` folder. This sample page shows an example of how to access and process PPP data from the state of Kentucky. We will then make a summary plot to look at the the amount small businesses received by gender. 

## Load data

The first thing to do is to load data from the Kentucky. Single state folders contain a .csv for small businesses who recieved loans up to 150k. Data for **ALL** states >150k should be downloaded from [here](https://www.dropbox.com/s/e7hfn71g0hnuelk/foia_150k_plus.csv?dl=0).

```{r load libraries}
library(data.table)
library(ggplot2)
```


```{r laod all data}
dataDir = 'data'
stateDir = 'Kentucky'

all_states_plus = fread(file.path(dataDir, 'foia_150k_plus.csv'))
ky_1 = fread(file.path(dataDir, stateDir, 'foia_up_to_150k_KY.csv'))
```

```{r head all_states_plus}
head(all_states_plus, 3)
```

```{r head kentucky only}
head(ky_1, 3)
```

There's a more information provided for busines that recieved more loans

## A Little Processing
```{r process_data}
all_states_plus[, BusinessName := NULL]
all_states_plus[, Address := NULL]
setnames(all_states_plus, 'LoanRange', 'LoanAmount')

ky_2 = all_states_plus[State == 'KY']
ky_dat = rbind(ky_1, ky_2)
```

## Make plot

```{r plot trend}
ggplot(ky_1, aes(x = Gender, y = LoanAmount, fill = Gender)) + geom_boxplot(alpha = 0.1) + theme(axis.text = element_text(color = 'black')) + labs(title = 'Small Business Loan Amount by Gender for Loans <150k')
```

